---
title: "Luisa M. Mimmi"
author:
  firstname: Luisa M.
  lastname: Mimmi
  address: Pavia, Italy
  position: "Economist | Policy Analyst | Freelance consultant"
  contacts:
    - icon: fa envelope
      text: lmm76@georgetown.edu
      url: "mailto:lmm76@georgetown.edu"
    - icon: assets/icon/bi-house-fill.svg
      text: luisamimmi.org
      url: https://luisamimmi.org
    # - icon: fa brands orcid
    #   text: 0000-0002-2244-8282
    #   url: https://orcid.org/0000-0002-2244-8282
    # - icon: fa brands x-twitter
    #   text: Lulliter
    #   url: https://x.com/Lulliter
    - icon: fa brands linkedin
      text: Luisa M. Mimmi
      url: https://www.linkedin.com/in/luisa-m-mimmi
    - icon: assets/icon/fa-google-scholar.svg
      text: Luisa M. Mimmi
      url: https://scholar.google.com/citations?user=OBYla5gAAAAJ&hl=en&oi=ao
    - icon: fa brands researchgate
      text: Luisa M. Mimmi
      url: https://www.researchgate.net/profile/Luisa-Mimmi
    - icon: fa brands github
      text: lulliter
      url: https://github.com/lulliter
style:
  color-accent: 0088cc #516db0
format:
  awesomecv-typst:
    font-paths: ["assets/fonts/"]
    keep-typ: true
execute: 
  echo: false
  warning: false
---

```{r}
# fonte 
# pckg https://kazuyanagimoto.com/typstcv/
# EXE https://kazuyanagimoto.com/cv/cv.pdf
# GH https://github.com/kazuyanagimoto/cv

# install.packages("typstcv", repos = "https://kazuyanagimoto.r-universe.dev")
library(typstcv)
library(dplyr)
library(stringr)
```

## Work Experience
```{r}
work <- readr::read_csv(here::here("data", "work.csv"), show_col_types = FALSE)%>% 
	#mutate(start_month = lubridate::month("start_month"))
	mutate(start  = glue::glue("{start_month}-{start_year}"),
			 end = glue::glue("{end_month}-{end_year}")) %>% 
	mutate(end = if_else(end == "NA-NA", "Present", end),
			 date = glue::glue("{start} - {end}")
	)

# names(work )
#work$end
```

```{r}
#| output: asis
work %>% 
	#typstcv::format_date(start_m_y_end_m_y, replace_na = "Present" ) %>% 
	#format_date(replace_na = , end = "end", sort_by = "start")  %>% 
	resume_entry(title = "title",
					 description = "org",
					 location = "where",
					 date = "date",
					 details = c("description_1" )
					 #details = c("description_1", "description_2" )
					 ) 
	
```


## Professional Skills
 
 •	<!-- \faIcon{calculator}--> Exceptional critical thinking, and **data analysis skills**, showcased in international development programs    
 •	<!-- \faIcon{sitemap}--> Demonstrated drive and resourcefulness in **leadership roles** for complex projects with multiple stakeholders      
 •	<!-- \faIcon{users}--> Effective **communication skills**, proven by record of multilingual publications and public speaking 

\newpage

## Education

```{r}
educ <- readr::read_csv(here::here("data", "edu.csv"), show_col_types = FALSE)
```

```{r}
#| output: asis
educ %>% 
mutate( end_m_y = glue::glue("{end_month} - {end_year}"))  %>% 
	resume_entry(title = "degree",
					 location = "inst",
					 date = "end_m_y",
					 description = "detail")
```
 


## Skills

```{r}
#| output: asis
read.csv("data/skill.csv") |>
  resume_entry(title = "area",
               description = "skills")
```


 
 
## Publications

### Peer-reviewed  


```{r}
# filter blogs
peer_pub <- RefManageR::ReadBib(
	file = here::here("data", "Lula-MyPublication-Narrow.bib"),
	.Encoding ="UTF-8")  %>%
	as.data.frame() %>%
	dplyr::filter(bibtype == "Article") # %>% 
	#mutate(url = if_else(is.na(url), url_preprint, url) )

```

```{r}
#| output: asis
peer_pub |>
	resume_entry(title = "title",
					 description =  "author",
					 location = "journaltitle",
					 date =  "date" ,
					 details = "url")
```


### Other Publications  
<br><br>

See complete list on  [**Google Scholar profile**](https://scholar.google.com/citations?user=OBYla5gAAAAJ&hl=en&oi=ao)

 
<!-- ### Blog posts -->
<!-- ```{r} -->
<!-- # filter blogs -->
<!-- lula_blog <- RefManageR::ReadBib( -->
<!--   file = here::here("data", "Lula-MyPublication-Narrow.bib"), -->
<!--   .Encoding ="UTF-8")  %>% -->
<!--   as.data.frame() %>% -->
<!--   dplyr::filter(bibtype  == "Online") -->
<!-- ``` -->

<!-- ```{r} -->
<!-- #| output: asis -->
<!-- lula_blog |> -->
<!-- 	resume_entry(title = "title", -->
<!-- 					 location = "type", -->
<!-- 					 description = "author", -->
<!-- 					 date = "date", -->
<!-- 					 details = "url") -->
<!-- ``` -->


<!-- ## Conference and Seminars  -->

<!-- ```{r} -->
<!-- # filter recent and....  -->
<!-- talks <- RefManageR::ReadBib( -->
<!-- 	file = here::here("data", "Lula-MyTalks.bib"), -->
<!-- 	.Encoding ="UTF-8")  %>% -->
<!-- 	as.data.frame() %>% -->
<!-- 	mutate(year = stringr::str_extract(date,pattern = "^.{1,4}")) %>%  -->
<!-- 	dplyr::filter(year >2020 & type != "Invited Talk") # %>%  -->
<!-- #mutate(url = if_else(is.na(url), url_preprint, url) ) -->

<!-- ``` -->

<!-- ```{r} -->
<!-- #| output: asis -->

<!-- talks %>% -->
<!-- 	resume_entry(title = "title",  -->
<!-- 					 date = "date" , -->
<!-- 					 description = "eventtitle",location = "venue" -->
<!-- 	) -->
<!-- ``` -->
